\documentclass[11pt,a4paper,sans]{moderncv} 
\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[scale=0.75]{geometry}
%------------------------------------------------------------
% Personal info
%------------------------------------------------------------
\firstname{Roman}
\familyname{Kashitsyn}

\title{Software Engineer}
\mobile{+7 910 396 3809}
\email{roman.kashitsyn@gmail.com}

\newcommand{\Cpp}{C{}\texttt{++}}

%------------------------------------------------------------
% Document
%------------------------------------------------------------
\begin{document}
\makecvtitle

%------------------------------------------------------------
% Skills
%------------------------------------------------------------
\section{Programming Skills}
\cvitem{Proficient}{\Cpp{}, C, Java}
\cvitem{Familiar}{Python, Go, Haskell, JavaScript, Scala}
\cvitem{Build Tools}{GNU make, CMake, Ant, Maven, Gradle}
\cvitem{OS}{GNU/Linux, Windows}
\cvitem{VCS}{git, svn}
\cvitem{Databases}{MongoDb, ZooKeeper, Redis, Oracle, Postgresql}
\cvitem{Other}{Multithreading, Concurrency, Algorithm Design,
API Design}

%------------------------------------------------------------
% Experience
%------------------------------------------------------------
\section{Experience}
\cventry{2013--Present}
{Software Engineer}
{Yandex -- Geodata Storage Team}
{Nizhny Novgorod}
{}
{ I worked on a system that maintains a catalog of companies (names,
  addresses, phones, etc.).  It's an internal service that is used by
  maps, search engine, online hotel booking, etc.  Keeping this data
  up to date is really important for millions of users.
  \newline{} I also worked on integration of the distributed task
  scheduling infrastructure developed in scope of the company catalog
  project into our internal maps editor application.
  \newline{} Now I'm working on tools that match related objects
  from different databases in order to improve our data integrity and,
  as result, our users' experience.
  \newline{}
Achievements:
\begin{itemize}
\item Designed and implemented a distributed service for asynchronous
  task processing in \Cpp{} using ZooKeeper and MongoDb. The service
  is designed to survive DC losses. It includes the scheduler process,
  cron-like process, worker API library, and RESTful
  HTTP--interface. The service has several internal users and reached
  production.
\item Designed and implemented \Cpp{} zookeeper client library leveraging
  \Cpp{}11 features on top of libzookeeper.
\item Designed and implemented \Cpp{} library to read/write CSV
  streams which is now heavily used in data exchange code. Initial
  draft of the implementation is available
  \href{https://github.com/roman-kashitsyn/text-csv}{on GitHub}.
\item Redesigned and rewrote existing build and packaging system using
  the Gradle build tool. It simplified the development and deployment
  cycle significantly.
\end{itemize}
}

\cventry{2012--2013}
{Lead Software Engineer}
{MFI Soft -- R\&D team}
{Nizhny Novgorod}
{}
{I worked on a prototype of a system that captures and analyzes HTTP
traffic running through a high-speed network interface.
\newline{}
Achievements:
\begin{itemize}
\item Designed and implemented a \Cpp{} library to store lots of small
  messages in large continuous memory-mapped chunks. The resulting
  library outperformed all the general-purpose storage systems we had
  tested for our use case.
\item Designed and implemented a \Cpp{} library to monitor the
  application statistics via a simple HTTP-interface.
\item Practiced code review, refactoring, unit-testing, and taught
  other engineers to use the best practices.
\item Made a lot of benchmarking, debugging, and optimization.
\end{itemize}
}

\cventry{2011--2012}
{Software Engineer, Architect}
{Exigen Services}
{Nizhny Novgorod}
{}
{I worked on a project for
\href{http://www.aaa.com/PPInternational/International.html}{AAA}
based on
\href{http://www.exigeninsurance.com/business-solutions/overview.html}{Exigen Insurance Solutions}.
The project was successfully deployed and transferred to support team.
\newline{}
Achievements:
\begin{itemize}
\item Led free Java and JavaScript courses for employees and external
  visitors.
\item Wrote a Maven2 plugin that significantly simplified work for
  translators.
\item Got ''Best Newcomer of the Year (2011)'' award.
\end{itemize}
}

\cventry{2010--2011}
{Software Engineer}
{IT Corp.}
{Nizhny Novgorod}
{}
{I worked on several projects for banks and public institutions. I
  also did various investigations, and prototypes.}

\cventry{2009--2010}
{Software Developer}
{Mera NN}
{Nizhny Novgorod}
{}
{I worked in a support team and made bugfixes and improvements in two
  projects:
\begin{itemize}
\item Adaptation of SS7 stack for Ericsson CPP platform (September
  2009--November 2010).  The system is mostly written in ANSI C and
  running on OSE Delta real-time OS.
\item Element Manager for Nortel ICP product (March 2009--September
  2009).  The product is based on Java 5 and J2EE and runs on JBoss
  4.2.
\end{itemize}
}

%------------------------------------------------------------
% Education
%------------------------------------------------------------
\section{Education}
\cventry{2004--2010}
{Specialist}
{N.I. Lobachevsky State University}
{Nizhny Novgorod}
{}
{Faculty of Computational Mathematics and Cybernetics.}

%------------------------------------------------------------
% Languages
%------------------------------------------------------------
\section{Languages}
\cvlanguage{English}{Fluent}{}
\cvlanguage{Russian}{Native}{}

%------------------------------------------------------------
% Profiles
%------------------------------------------------------------
\section{Profiles}
\cvitemwithcomment{GitHub}{\url{https://github.com/roman-kashitsyn}}{}
\cvitemwithcomment{Shelfari}{\url{http://www.shelfari.com/lifted}}{}
\cvitemwithcomment{LinkedIn}{\url{https://www.linkedin.com/profile/view?id=193829212}}{}

%------------------------------------------------------------
% Interests
%------------------------------------------------------------
\section{Interests}
\cvlistdoubleitem{Software Architecture}{API Design}
\cvlistdoubleitem{Functional Programming}{Physics}
\cvlistdoubleitem{Build Systems}{Math}

\end{document}
