\begin{rubric}{Employment History}

\entry*[\timekey{October 2012}{Now}]
  \parbox{\EmpHistoryBlock}{
  \textbf{MFI Soft}\\
  \textit{Lead Software Engineer}\\
  I am a software engineer in the SORM project. I design and implement
  complex system components in appropriate programming language
  (C/C++, Java or Python). At the moment I've designed and implemented
  (mostly alone) two components: library for small binary objects
  packing and a library for run-time software system diagnostics
  (lightweight JMX analogue for C++). I perform code review and
  refactoring, implement unit-tests and benchmarks, optimize
  various parts of the product.
  }


  \entry*[\timekey{August 2011}{October 2012}]
  \parbox{\EmpHistoryBlock}{
  \textbf{Exigen Services}\\
  \textit{Software Engineer, Architect}\\
  I was a software engineer in AAA and Industrial Alliance projects
  based on EIS
  (\url{http://www.exigeninsurance.com/business-solutions/overview.html}).
  I worked on external services integration: implemented batch jobs to
  communicate with 3rd party systems via XML files stored in remote
  FS, caching and maping of provided data into core data structures. I
  fixed bugs in various parts of the system and wrote several
  Liquibase scripts for DB update.  I've also written and documented a
  maven plugin to simplify products localization.  Unit testing was a
  major part of daily work.  We used scrum-like development process.
  I also taught Java, JavaScript and Spring Framework on internal and
  external trainings.
  }

  \entry*[\timekey{November 2010}{August 2011}]
  \parbox{\EmpHistoryBlock}{
  \textbf{IT Corp.}\\
  \textit{Software Engineer}\\
  I was a software engineer and participated in several projects.  I
  have implemented major parts of information system for Russian
  Pension Fund.  The project is based on Grails Framework and written
  mostly in Groovy programming language.
  I have configured WCM modules for Exo and WebSphere portal
  platforms for several corporate portals and written custom modules for
  Bitrix platform on PHP.
  I was lead java-developer of the ''Gamma'' project for Sberbank~---
  authentication and authorization system for internal use. Proposed
  architecture integrates EJB 2.1 (legacy exposed interface) and EJB 3
  (newly created modules) and use JPA layer to map
  users/roles/permissions tables into java objects. I have proposed and
  documented (with simple Markdown files) the architecture, wrote
  build script with Ant, made JPA entity definition, implemented JPA
  queries, EJB 2.1/3 integration code and simple module tests.
  }

  \entry*[\timekey{September 2009}{November 2010}]
  \parbox{\EmpHistoryBlock}{
  \textbf{Mera NN}\\
  \textit{Software designer}\\
  I was a software designer in Tieto CPP project~--- an adaptation of
  multiplatform SS7 stack for Ericsson CPP platform. The application
  is written in ANSI C and running under OSE Delta operating
  system. During my work in this project I designed and implemented
  code improvements and component tests, analyzed trouble requests,
  wrote routines for Automatic Upgrade Engine to update database via
  ODBC, answered customer's questions, maintained project
  documentation, calculated code coverage by Rational Test RealTime
  tool and checked memory usage by Rational Purify tool, took exams
  at the new staff.
  }

  \entry*[\timekey{March 2009}{September 2009}]
  \parbox{\EmpHistoryBlock}{
  \textbf{Mera NN}\\
  \textit{Software developer}\\
   I was a software developer in the Element Manager project~--- a
   web-application for operating, administering and maintaining the
   Nortel ICP product (\url{http://www.nortel.com/icp}). It is based on
   Java 5 and J2EE technologies and runs on the JBoss 4.2 application
   server. Eclipse and MyEclipse IDE were used for
   development. During my work in this project, I designed JSF pages,
   JavaScript routines, JSF beans, data access objects based on
   Hibernate. I ran Ant build scripts to compile and build the code. I
   used Ajax4JSF and RichFaces JSF tag libraries to add Ajax support
   to the JSF pages.
  }
\end{rubric}
